---
title: "Appendix A: Supplementary Materials"
---

# Appendix A: Supplementary Materials

This appendix contains supplementary materials and additional analyses for the NIH grant progress reports.

## Extended Methods

### Neuroimaging Data Acquisition

All MRI data were collected on a 3T Siemens Prisma scanner with a 64-channel head coil. Functional MRI data were acquired using a multiband echo-planar imaging (EPI) sequence with the following parameters:

- TR = 800 ms
- TE = 30 ms
- Flip angle = 52°
- Multiband factor = 6
- FOV = 208 × 208 mm
- Matrix size = 104 × 104
- 72 slices (2 mm isotropic)
- 500 volumes per run

Participants completed 4 runs of each cognitive control task, with each run lasting approximately 6-7 minutes. High-resolution T1-weighted structural images were acquired using an MPRAGE sequence (TR = 2400 ms, TE = 2.22 ms, TI = 1000 ms, flip angle = 8°, 0.8 mm isotropic voxels).

### EEG Data Acquisition

Simultaneous EEG data were recorded using a 64-channel MR-compatible EEG system (Brain Products GmbH) with FCz as the reference electrode. Data were digitized at 5000 Hz with a 0.1-250 Hz bandpass filter. MR gradient artifact correction was performed using a template subtraction method, and cardioballistic artifacts were removed using independent component analysis (ICA).

## Extended Results

### Additional Behavioral Analyses

```{r}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(kableExtra)

# Simulate behavioral data
set.seed(456)

behavioral_data <- tibble(
  Group = rep(c("TD", "ADHD", "ASD"), each = 50),
  Age = c(
    round(runif(50, 7, 18), 1),
    round(runif(50, 7, 18), 1),
    round(runif(50, 7, 18), 1)
  ),
  SSRT = c(
    rnorm(50, 250, 30),
    rnorm(50, 290, 40),
    rnorm(50, 280, 35)
  ),
  GoRT = c(
    rnorm(50, 450, 50),
    rnorm(50, 480, 70),
    rnorm(50, 470, 60)
  ),
  GoAccuracy = c(
    rbeta(50, 85, 15) * 100,
    rbeta(50, 80, 20) * 100,
    rbeta(50, 82, 18) * 100
  ),
  StopAccuracy = c(
    rbeta(50, 50, 50) * 100,
    rbeta(50, 45, 55) * 100,
    rbeta(50, 48, 52) * 100
  )
)

# Calculate summary statistics
summary_stats <- behavioral_data %>%
  group_by(Group) %>%
  summarize(
    n = n(),
    `Age (Mean ± SD)` = paste0(round(mean(Age), 1), " ± ", round(sd(Age), 1)),
    `SSRT (ms)` = paste0(round(mean(SSRT), 1), " ± ", round(sd(SSRT), 1)),
    `Go RT (ms)` = paste0(round(mean(GoRT), 1), " ± ", round(sd(GoRT), 1)),
    `Go Accuracy (%)` = paste0(
      round(mean(GoAccuracy), 1),
      " ± ",
      round(sd(GoAccuracy), 1)
    ),
    `Stop Accuracy (%)` = paste0(
      round(mean(StopAccuracy), 1),
      " ± ",
      round(sd(StopAccuracy), 1)
    )
  )

# Create formatted table
kable(
  summary_stats,
  caption = "Table A1: Behavioral performance on the Stop Signal Task by group.",
  align = "lccccc"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  )
```

### Age Effects on Task Performance

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 9
#| fig-height: 4
#| fig-cap: "Figure A1: Age effects on Stop Signal Reaction Time (SSRT) by group."

ggplot(behavioral_data, aes(x = Age, y = SSRT, color = Group)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  labs(
    title = "Age Effects on Stop Signal Task Performance",
    x = "Age (years)",
    y = "Stop Signal Reaction Time (ms)",
    color = "Group"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  )
```

### Group Differences in Neural Activation

The following table summarizes the significant clusters of activation during successful stop trials versus go trials for each group. Only clusters surviving FWE correction (p < 0.05) at the cluster level are reported.

```{r}
#| echo: false
#| warning: false
#| message: false

# Create table of activation clusters
activation_clusters <- tibble(
  Group = c(
    "TD",
    "TD",
    "TD",
    "TD",
    "ADHD",
    "ADHD",
    "ADHD",
    "ASD",
    "ASD",
    "ASD",
    "ASD"
  ),
  Region = c(
    "Right Inferior Frontal Gyrus",
    "Right Middle Frontal Gyrus",
    "Right Insula",
    "Anterior Cingulate Cortex",
    "Right Inferior Frontal Gyrus",
    "Right Insula",
    "Anterior Cingulate Cortex",
    "Right Inferior Frontal Gyrus",
    "Right Middle Frontal Gyrus",
    "Posterior Parietal Cortex",
    "Anterior Cingulate Cortex"
  ),
  `Cluster Size` = c(
    342,
    256,
    189,
    210,
    185,
    124,
    167,
    267,
    198,
    315,
    176
  ),
  `Peak Z-score` = c(
    5.8,
    5.2,
    4.9,
    5.1,
    4.3,
    3.9,
    4.2,
    5.1,
    4.6,
    5.7,
    4.4
  ),
  `MNI Coordinates` = c(
    "48, 16, -4",
    "44, 38, 28",
    "34, 22, -2",
    "6, 24, 38",
    "46, 14, -6",
    "36, 20, -4",
    "4, 22, 36",
    "48, 18, -2",
    "42, 36, 26",
    "36, -52, 48",
    "4, 26, 34"
  )
)

# Create formatted table
kable(
  activation_clusters,
  caption = "Table A2: Significant activation clusters during stop > go contrast by group.",
  align = "lllcc"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  ) %>%
  pack_rows("Typically Developing", 1, 4) %>%
  pack_rows("ADHD", 5, 7) %>%
  pack_rows("ASD", 8, 11)
```

## Additional Analyses in Progress

The following additional analyses are currently in progress and will be included in future reports:

1. **Developmental Trajectory Modeling**: We are applying mixed-effects modeling to characterize nonlinear developmental trajectories of neural activation and connectivity patterns.

2. **Sex Differences Analysis**: We are examining potential sex differences in neural signatures of cognitive control across the three diagnostic groups.

3. **Computational Modeling Extensions**: We are expanding our computational modeling approach to incorporate trial-by-trial dynamics and reinforcement learning parameters.

4. **Longitudinal Prediction Analysis**: We are beginning to analyze the predictive utility of baseline neural measures for cognitive and behavioral outcomes at follow-up.
