---
title: "Appendix B: Extended Data Tables and Figures"
---

# Appendix B: Extended Data Tables and Figures

This appendix contains additional data tables and figures that supplement the main progress report.

## Extended Demographic Information

```{r}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(kableExtra)

# Simulate demographic data
set.seed(789)

demographic_data <- tibble(
  Group = rep(c("Typically Developing", "ADHD", "ASD"), each = 1),
  n = c(48, 52, 45),
  `Age Range` = c("7.2 - 17.9", "7.4 - 18.0", "7.1 - 17.6"),
  `Age (Mean ± SD)` = c("12.4 ± 3.2", "12.1 ± 3.5", "11.8 ± 3.3"),
  `Sex (M/F)` = c("25/23", "34/18", "32/13"),
  `IQ (Mean ± SD)` = c("112.3 ± 12.5", "108.6 ± 13.2", "106.8 ± 15.4"),
  `SES (Mean ± SD)` = c("46.8 ± 11.2", "43.2 ± 12.5", "44.5 ± 13.1"),
  `Medication (%)` = c("0%", "68%", "42%"),
  `Comorbidities (%)` = c("0%", "54%", "63%")
)

# Create extended demographic table
kable(
  demographic_data,
  caption = "Table B1: Extended demographic information for study participants.",
  align = "lcccccccc"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    position = "center"
  )
```

*Note: SES = Socioeconomic Status measured using the Hollingshead Four-Factor Index of Social Status. Medication refers to current psychotropic medication use. Comorbidities include anxiety disorders, mood disorders, learning disabilities, and other neurodevelopmental conditions.*

## Medication Status Details

```{r}
#| echo: false
#| warning: false
#| message: false

# Create medication details table
medication_data <- tibble(
  Medication = c(
    "Stimulants",
    "Selective Serotonin Reuptake Inhibitors (SSRIs)",
    "Alpha-2 Agonists",
    "Atypical Antipsychotics",
    "Atomoxetine",
    "Other"
  ),
  `ADHD Group (n=52)` = c(
    "28 (53.8%)",
    "8 (15.4%)",
    "7 (13.5%)",
    "4 (7.7%)",
    "6 (11.5%)",
    "3 (5.8%)"
  ),
  `ASD Group (n=45)` = c(
    "8 (17.8%)",
    "12 (26.7%)",
    "5 (11.1%)",
    "7 (15.6%)",
    "2 (4.4%)",
    "5 (11.1%)"
  )
)

kable(
  medication_data,
  caption = "Table B2: Medication status of ADHD and ASD participants.",
  align = "lcc"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  ) %>%
  add_footnote(
    "Note: Some participants were taking multiple medications, so percentages may sum to >100%.",
    notation = "symbol"
  )
```

## Extended Task Performance Data

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 10
#| fig-height: 6
#| fig-cap: "Figure B1: Performance on multiple cognitive control tasks across groups."

# Simulate task performance data
set.seed(123)
n_per_group <- 50

task_data <- tibble(
  ID = 1:(n_per_group * 3),
  Group = rep(c("Typically Developing", "ADHD", "ASD"), each = n_per_group),

  # Stop Signal Task
  SST_SSRT = c(
    rnorm(n_per_group, 250, 30), # TD
    rnorm(n_per_group, 290, 40), # ADHD
    rnorm(n_per_group, 280, 35) # ASD
  ),

  # Flanker Task
  Flanker_RT_Diff = c(
    rnorm(n_per_group, 60, 20), # TD
    rnorm(n_per_group, 85, 25), # ADHD
    rnorm(n_per_group, 75, 22) # ASD
  ),

  # Task Switching
  Switch_Cost = c(
    rnorm(n_per_group, 150, 40), # TD
    rnorm(n_per_group, 200, 50), # ADHD
    rnorm(n_per_group, 190, 45) # ASD
  ),

  # Working Memory Task
  WM_Accuracy = c(
    rbeta(n_per_group, 8, 2) * 100, # TD
    rbeta(n_per_group, 6, 3) * 100, # ADHD
    rbeta(n_per_group, 7, 3) * 100 # ASD
  )
)

# Prepare for visualization
task_long <- task_data %>%
  pivot_longer(
    cols = c(SST_SSRT, Flanker_RT_Diff, Switch_Cost, WM_Accuracy),
    names_to = "Task",
    values_to = "Performance"
  ) %>%
  mutate(
    Task = factor(
      case_when(
        Task == "SST_SSRT" ~ "Stop Signal Task\n(SSRT, ms)",
        Task == "Flanker_RT_Diff" ~ "Flanker Task\n(Interference Effect, ms)",
        Task == "Switch_Cost" ~ "Task Switching\n(Switch Cost, ms)",
        Task == "WM_Accuracy" ~ "Working Memory\n(Accuracy, %)"
      ),
      levels = c(
        "Stop Signal Task\n(SSRT, ms)",
        "Flanker Task\n(Interference Effect, ms)",
        "Task Switching\n(Switch Cost, ms)",
        "Working Memory\n(Accuracy, %)"
      )
    )
  )

# Create visualization
ggplot(task_long, aes(x = Group, y = Performance, fill = Group)) +
  geom_violin(alpha = 0.7, scale = "width") +
  geom_boxplot(width = 0.2, alpha = 0.5, outlier.shape = NA) +
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 23,
    size = 3,
    fill = "white"
  ) +
  scale_fill_viridis_d(option = "plasma", end = 0.8) +
  facet_wrap(~Task, scales = "free_y") +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  labs(
    title = "Performance Across Multiple Cognitive Control Tasks",
    x = NULL,
    y = NULL,
    fill = "Group"
  )
```

*Note: For Stop Signal Task, Flanker Task, and Task Switching, lower values indicate better performance. For Working Memory Task, higher values indicate better performance.*

## Correlation Matrix

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 7
#| fig-cap: "Figure B2: Correlation matrix of behavioral measures and neural activation in key regions of interest."

library(corrplot)

# Simulate correlation data
set.seed(456)

# Create correlation matrix with realistic relationships
cor_matrix <- matrix(
  c(
    # SST_SSRT
    1.00,
    0.42,
    0.38,
    -0.35,
    0.45,
    -0.52,
    0.33,
    -0.28,

    # Flanker_RT_Diff
    0.42,
    1.00,
    0.44,
    -0.31,
    0.29,
    -0.38,
    0.25,
    -0.22,

    # Switch_Cost
    0.38,
    0.44,
    1.00,
    -0.40,
    0.32,
    -0.35,
    0.27,
    -0.30,

    # WM_Accuracy
    -0.35,
    -0.31,
    -0.40,
    1.00,
    -0.26,
    0.48,
    -0.23,
    0.41,

    # rIFG_Activation
    0.45,
    0.29,
    0.32,
    -0.26,
    1.00,
    -0.45,
    0.58,
    -0.33,

    # ACC_Activation
    -0.52,
    -0.38,
    -0.35,
    0.48,
    -0.45,
    1.00,
    -0.36,
    0.50,

    # Striatum_Activation
    0.33,
    0.25,
    0.27,
    -0.23,
    0.58,
    -0.36,
    1.00,
    -0.29,

    # DLPFC_Activation
    -0.28,
    -0.22,
    -0.30,
    0.41,
    -0.33,
    0.50,
    -0.29,
    1.00
  ),
  nrow = 8,
  byrow = TRUE
)

# Column and row names
colnames(cor_matrix) <- rownames(cor_matrix) <- c(
  "SST (SSRT)",
  "Flanker Effect",
  "Switch Cost",
  "WM Accuracy",
  "rIFG Activation",
  "ACC Activation",
  "Striatum Activation",
  "DLPFC Activation"
)

# Plot correlation matrix
corrplot(
  cor_matrix,
  method = "color",
  type = "upper",
  order = "hclust",
  tl.col = "black",
  tl.srt = 45,
  addCoef.col = "black",
  col = colorRampPalette(c(
    "#2166AC",
    "#D1E5F0",
    "#FFFFFF",
    "#FDDBC7",
    "#B2182B"
  ))(200),
  diag = FALSE,
  tl.cex = 0.8,
  cl.cex = 0.8,
  number.cex = 0.7,
  title = "Correlation Matrix of Behavioral and Neural Measures",
  mar = c(0, 0, 2, 0)
)
```

*Note: Correlations are based on data from all participants (N = 145). rIFG = right inferior frontal gyrus, ACC = anterior cingulate cortex, DLPFC = dorsolateral prefrontal cortex.*

## Neural Network Analysis Results

```{r}
#| echo: false
#| warning: false
#| message: false

# Create network analysis results table
network_results <- tibble(
  `Network Metric` = c(
    "Global Efficiency",
    "Local Efficiency",
    "Modularity (Q)",
    "Small-worldness",
    "Frontoparietal-Default Mode Connectivity",
    "Frontoparietal-Salience Connectivity",
    "Salience-Default Mode Connectivity"
  ),
  `Typically Developing` = c(
    "0.42 ± 0.05",
    "0.64 ± 0.07",
    "0.38 ± 0.04",
    "1.74 ± 0.23",
    "-0.12 ± 0.08",
    "0.35 ± 0.07",
    "-0.08 ± 0.06"
  ),
  `ADHD` = c(
    "0.38 ± 0.06*",
    "0.59 ± 0.08*",
    "0.34 ± 0.05*",
    "1.56 ± 0.25*",
    "-0.07 ± 0.09*",
    "0.28 ± 0.08*",
    "-0.04 ± 0.07*"
  ),
  `ASD` = c(
    "0.39 ± 0.06*",
    "0.61 ± 0.07",
    "0.31 ± 0.06**",
    "1.62 ± 0.24*",
    "-0.02 ± 0.08**",
    "0.30 ± 0.07*",
    "0.01 ± 0.08**"
  )
)

kable(
  network_results,
  caption = "Table B3: Brain network metrics during cognitive control by group.",
  align = "lccc"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    position = "center"
  ) %>%
  add_footnote(
    c(
      "Values are presented as mean ± standard deviation.",
      "* p < 0.05, ** p < 0.01 compared to Typically Developing group, FDR-corrected for multiple comparisons."
    ),
    notation = "symbol"
  )
```

## Future Analyses

The following additional analyses will be conducted in the next phase of the project:

1. **Multivariate Pattern Analysis (MVPA)**: We will apply MVPA techniques to identify distributed patterns of neural activity that differentiate between successful and unsuccessful inhibition trials, as well as between diagnostic groups.

2. **Dynamic Connectivity Analysis**: We will examine time-varying changes in functional connectivity during cognitive control tasks using sliding window approaches and dynamic causal modeling.

3. **Integration with Genetic Data**: For a subset of participants with available genetic data (N = 68), we will explore associations between polygenic risk scores for ADHD/ASD and neural signatures of cognitive control.

4. **Machine Learning Prediction Models**: We will develop and validate machine learning models to predict individual differences in cognitive control abilities based on multimodal neuroimaging features, with the goal of identifying potential biomarkers for early intervention.

These analyses will be included in future progress reports as they are completed.
